---
title: "Lab 8"
author: "Amanda Murphy"
date: "11/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
x <- 1
u <- 0
sigma <- 1

1/(sigma*sqrt(2*pi)) * exp(1)^(-.5*((x-u/sigma)^2))

dnorm(1,0,1)

```


1. Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of zscores. (1 point).



```{r}
to_zscores <- function(raw,mu,sd){
  zscores <- return((raw-mu)/sd)
  return(zscores)
}

some_numbers<- c(2,5,6,7,8)

to_zscores(some_numbers,5,1)

to_zscores_b <- function(raw,mu=NULL,sdev=NULL){
  if(is.null(mu) == TRUE) mu <- mean(raw)
  if(is.null(sdev) == TRUE) sdev <- sd(raw)
  zscores <- (raw-mu)/sdev
  return(zscores)
  
}

 to_zscores_b(some_numbers,mu =5, sdev=1)
  
  to_zscores_b(some_numbers)
  

```

-- Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.

-- Advanced: Have an option so that the function will convert the raw scores to zscores in one of two ways:
using user provided mean and standard deviation
using the calculated mean and standard deviation from the raw scores



2. Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution. (2 points).



```{r}
z.test <- function(sample_mean,sample_size,mu,sigma){
  smpl_dist_mean <- mu
  smpl_dist_sd <- sigma/sqrt(sample_size)
  
  p_value <- pnorm(sample_mean,smpl_dist_mean,smpl_dist_sd, lower.tail = FALSE)
  return(p_value)
  
}

z.test(sample_mean=50, 
       sample_size = 25,
       mu = 40,
       sigma = 7)


z.test(1,1,0,1)

z.test(25,100,18,4)


```


-- Use your z-test function to conduct a test of the following. A sample of 25 scores is taken. The mean of the sample is 50. The sample is assumed to have been taken from a normal distribution with mean 40 and standard deviation 7. Report a one-tailed z-test, examining the probability of obtaining a sample of greater than 50 in this situation. Report the results, and give a brief sentence explaining the result and the inference you make (2 points).


### With a sample mean of 50 compared to the population mu being 40 with a standard deviation of 7, the pvalue is very small, meaning that it would be rare or a very small probability percentage that your sample results would give you a mean of 50. ** This example kind of confused me bc I would think if sigma was 7 then one standard deviation away from the mean would be 47 and that is only three less than the sample mean we found. I guess maybe I am thinking in terms of our own sample standard deviation, rather than the standard error.